\chapter*{Acknowledgements}

Firstly, I would like to thank the Federal Government for their generous
support of my PhD in the form of the Australian Postgraduate Award scholarship.
I would also like to thank the University of Sydney and particularly the School
of Mathematics and Statistics for providing support through the opportunity
tutor and lecturer statistics and mathematics subjects within the School.

Thanks to Professor Samuel M\"ueller for providing excellent advice and the
opportunity to tutor STAT3012.  Thanks also to Professor Jean Yang
 and the Bioinformatics research group at the University of Sydney for the
 stimulating research meetings, friendliness and company. Especially thanks for the Thai
 lunches and the pizza! I've learned a lot from all of you.  Special thanks to
 Kevin Wang for your boundless enthusiasm and inspiration, your offbeat sense of
 humour, and the very insightful discussions we've had regarding \texttt{tidyverse}
 and \texttt{ggplot2}.

To my family --  Charles, Eleanor, and Ben: Thank you for all your love and support
during this sometimes challenging period.

To Charles Gray, who I met at the AMSI Summer School in 2014. Thanks for the
supportive chats and the opportunity to stay with you. I look forward to
reading your thesis with great interest, and sharing many \texttt{tidyverse}
adventures with you in the future.

To Sarah Romanes and especially the ever patient Weicheng Yu -- Thanks for
reading and offering feedback on drafts of this thesis while I was writing up.
I'll be sure to return the favour when the time comes. Extra thanks to Weicheng
as a fellow denizen of Carslaw 807a for many interesting mathematical and
statistical discussions, and always providing a friendly ear when my editing
wasn't going well or my programs were crashing.

Last, but by no means least, my most sincere and humble thanks to my supervisor
and friend Dr John Ormerod. Thanks for introducing me to the exciting world of
computational Bayesian statistics and numerics. For always taking the time to
explain difficult theoretical concepts, the endless good recommendations of
papers and books to read, and teaching me the fine art of mathematical writing
and editing.  On a personal level, thanks for your seemingly limitless patience
and understanding. I've learned a great deal from you over the past
half-decade, and some of it even had to do with statistics!
