\documentclass{letter}
\begin{document}

Dear Dr Andrew Zangion,

I'm writing to apply for the project work in spatial statistics advertised on the anzstat mailing list on
June 14th, 2017.

I feel I have the required skills to complete the project.
As part of my ongoing PhD work with Dr John Ormerod, I have learned about Bayesian methodology, particularly
MCMC and Variational Bayes. I learned about maximum likelihood in my undergraduate degree.
In order to perform numerical experiments to test our ideas, I've modified and developed thousands of lines
of well-commented, modular R code implementing the models in our work.
When some sections of code were found to be performance bottlenecks, they were re-written in
C++ using the Rcpp and the Armadillo and Eigen libraries, and parallelised with OpenMP.
This code was documented in draft papers which we are preparing for submission.

My education includes a Bachelor's Degree in Computer Science, a Bachelor of Science (Pure Mathematics and
Mathematical Statistics) with first class Honours, a Masters of Biostatistics and an ongoing PhD in computational 
statistics with Dr John Ormerod on variational approximations. I am in the final year of my PhD,
and plan to submit my thesis at the end of the year. My PhD work involves writing R and C++ code to perform
numerics and matrix computations.

In between my Computer Science and Mathematics degrees, I spent nine years working as a programmer on
a variety of projects.
I'm am used to collaborating with other programmers, and using version control systems such as GitHub and
remote collaboration tools such as Slack and Skype.

My reference is my PhD supervisor, Dr John Ormerod. His email address is john.ormerod@sydney.edu.au, and his
phone number is 02 9351 5883.

Yours, \\
Mark Greenaway

\end{document}