% Chapter_3_normal_linear_models_numerical_issues.tex

\documentclass{amsart}[12pt]
% \documentclass[times, doublespace]{anzsauth}

\addtolength{\oddsidemargin}{-.75in}%
\addtolength{\evensidemargin}{-.75in}%
\addtolength{\textwidth}{1.5in}%
\addtolength{\textheight}{1.3in}%
\addtolength{\topmargin}{-.8in}%
\addtolength{\marginparpush}{-.75in}%
% \setlength\parindent{0pt}
% \setlength{\bibsep}{0pt plus 0.3ex}

% \usepackage[authoryear]{natbib}
\usepackage{graphicx}
\usepackage{algorithm,algorithmic}
\usepackage{cancel}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{algorithm,algorithmic}
\usepackage[inner=2.5cm,outer=1.5cm,bottom=2cm]{geometry}
\usepackage{setspace}
\onehalfspacing
\usepackage{microtype}
\usepackage{color}

\newtheorem{theorem}{Theorem}[section]

\title{Chapter 3 Variational Bayes for Linear Model Selection using Mixtures of g-priors -- Numerical issues}
\author{Mark Greenaway, John T. Ormerod}

\input{include.tex}
\input{Definitions.tex}

\newcommand{\mgc}[1]{{\color{blue}#1}}
\newcommand{\joc}[1]{{\color{red}#1}}

\begin{document}

\maketitle

$\tau_g$

\mgc{Trapezoidal integration for $\E[g | \vy]$, choose points for function evaluation, how many and where. Use
John's Z\_g\_trapint code, which does clever things to find the endpoints of integration.
}
In order to evaluate the expression $\E[g | \vy]$, we must numerically evaluate the integral

\[
	\int_0^\infty \frac{(1-R^2)^{b+1} g^{b+1} [1 + g(1 - R^2)]^{-n/2}}{\Beta(p/2 + a + 1, b + 1)} dg
\]

using trapezoidal integration. The integrand consists of a constant mulitplied by a rational function of g. As
b is a function of n, for large values of n both the numerator and the denominator become very large, leading
to possible floating point overflow and underflow for the denominator.

We avoid these numerical issues by computing the integrand on the log scale. As a function of g, the integrand
is proportional to

\[
	(b + 1) \log{g} - n / 2 \log{[1 + g(1 - R^2)]}.
\]

$\log{g}$ and $\log{[1 + g(1 - R^2)]}$ will be similiar in magnitude, $\BigO{(\log{g})}$, while the
co-efficients will be $\BigO{(n)}$. This suggests the integrand will be $\BigO{(1)}$.

\begin{align*}
	&\left[\frac{g}{1 + g(1 - R^2)}\right]^{n/2} g^{-p/2 -a - 1} \\
	=&(1 - R^2)^{-1} \underbrace{\left[\frac{g(1 - R^2)}{1 + g(1 - R^2)}\right]^{n/2}}_{ \leq 1} g^{-p/2 - a - 1}
\end{align*}

So in fact the integrand is $\BigO{(g^{-p/2 - a - 1})}$, and so the integral is convergent and numerical
integration will be numerically well-behaved.

\mgc{Accuracy of g. 10,000 grid points between 0 and 10. Functions exponentially decrease to 0 monotonically
outside of this interval.
}

The accuracy of g was assessed using the expression

\[
	1 - \int_0^\infty |p(g | \vy) - q(g)| dg,
\]

where $q(g)$ was evaluated using trapezoidal integration. To find the end-points between which to numerically
integrate \ldots

\mgc{Accuracy of $\sigma^2$, identities for $_1 F_2$ allow us to avoid overflows and numerically evaluate the
accuracy integral. 1,000 grid points spread between 0 and 10. Functions exponentially decrease to 0
monotonically outside of this interval.
}

The expression $_1 F_1\left (b + 1; n/2; nR^2/(2 \sigma^2) \right)$ in the posterior
probability for $\sigma^2$ frequently overflowed. To avoid this numerical difficulty, we used the transformation

\[
	e^x _1 F_1(a; b; -x) = _1 F_1(b - a; b; x)
\]

and performed our calculation of the posterior probablity on the log-scale, exponentiating only at the end.
On some occasions, this expression would overflow, and we would then fall back to the original expression.

\mgc{
Precision, identities for $_2 F_1$ allow us to avoid underflow and numerically evaluate the expression.
}

The expression

\[
	_2 F_1(n/2 + 1, b + 1, n/2; R^2)
\]

would often numerically overflow when evaluated using \texttt{gsl\_sf\_hyperg\_2F1} from the GNU Scientific
Library. To cirumvent this difficulty, we made use of Euler's transformation

\[
	_2 F_1(a, b, c; z) = (1 - z)^{c - a - b} _2 F_1 (c - a, c - b, c; z)
\]

so that

\[
	_2 F_1(n/2 + 1, b + 1, n/2; R^2) = _2 F_1(-1, n/2 - b - 1, n/2; R^2) (1 - R^2)^{-b-2}.
\]

The advantage of this transformation is that while $_1 F_2$ is defined as an infinite series when the first
and second arguments to $_2 F_1$ is positive, when either of them are negative, it becomes a polynomial. This
is much easier to evaluate numerically.

We work on the log scale to avoid one part of an expression overflowing and another part underflowing. Working
on the log scale leads to working with numbers which are smaller in magnitude, which avoids floating point
overflow and underflow. The large positive and negative logs of the terms in the expressions then have the
opportunity to additively cancel, and we can then exponentiate the resulting value to complete the
calculation. The price that we pay is the loss of accuracy from taking logs of the terms and then
exponentiating.

\bibliographystyle{elsarticle-harv}
\bibliography{references_mendeley}

\end{document}