%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                   %
%   University of New South Wales letter template   %
%                                                   %
%      Customized for M.P. Wand                     %
%                                                   %  
%       Last changed: 14th January, 2003            %
%                                                   %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\documentclass[11pt]{article}
\usepackage{graphicx,verbatim,amsfonts}

\include{GrandMacros}
\include{BibMacros}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{geometry}
\geometry{verbose,a4paper,tmargin=1in,bmargin=1.5in,lmargin=1in,rmargin=1in}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\rightline{\today}

\noindent Journal of Graphical and Computational Statistics \\



 
 

\vskip5mm \noindent To the Editors,

\vskip5mm \noindent Could you please consider our paper:
\vskip5mm
\centerline{\bf Numerical aspects of Bayesian linear model averaging using mixture $g$-priors}
\medskip 
 
\vskip5mm
\centerline{\sf by Mark Greenaway and John T. Ormerod}

\vskip5mm \noindent for publication in the {\it Journal of Graphical and Computational Statistics}?



\medskip 
In this article, we report on Bayesian linear model averaging using new analytic expressions for Bayes factors when under several mixture $g$-priors, usually in terms of the Gaussian hypergeometric function.
We derive numerically stable methods for evaluating these Bayes factors.
This is significant because it leads to the most efficient
and numerically stable approach to exact Bayesian model averaging
to date. We develop an R package implementing these ideas,
which is available on GitHub which exploits parallel computation.
Our package outperforms other Bayesian model averaging software
in the literature on several standard example data sets. 



\medskip 
The paper should be of interest to readers in the area of Bayesian model selection
and Bayesian model averaging.


\medskip 
Finally, we confirm that this work is original and has not been published elsewhere nor is it currently under
consideration for publication elsewhere.


\vskip5mm \noindent We eagerly await your response.

\vskip5mm \noindent Yours sincerely,

\vskip5mm \noindent Mark Greenaway and John T. Ormerod
\end{document}
