\documentclass{amsart}
\usepackage{tikz}
\title{Meeting with Dr John Ormerod - 16/02/2016}

\input{Definitions.tex}

\begin{document}

\maketitle

Time: 11:45am to 12:30pm \\
Attendees: Dr John Ormerod, Mark Greenaway \\
 \\
Refine propject plan, track progress. \\
Code $\mC = [\mX, \mZ]$. \\
Start calculating mean field updates for VB approximation. \\
Code to calculate $D_{ij}$ matrix should be written in the future. We need it for CVB, not now. \\

\section{Testing}
Correlations code \\
 \\
minimal test case passes \\
if we matched Hitters.Rs, that would be an acceptable black box test. \\
\texttt{ZE.exact.slow}'s $R^2$ would be the best test, as it's using lm(), not any of our code. \\
unit test rank one updates and downdates \\
\texttt{ZE.exact.fast} avoids re-allocating matrices for $A$ matrix, approximately 8 times faster. \\
The closer $R^2$ gets to 1, the more accuracy matters, as we're going to be calculating $\log (1 - R^2)$. \\
4 decimal places. \\

\section{Literature to read this week}
\begin{enumerate}
\item Read ``Mixtures of g priors for Bayesian Variable Selection''. \\
Priors avoid Bartlett's paradox and the information paradox. \\
Lack of consistency under the null model mentioned \\
g controls model selection \\
g controls model selection \\
Consistent, as $n \to \infty$ true model will dominate the posterior \\
Look at Numerical Recipes Gaussian hypergeometric function section \\
Recent paper in The American Statistician on hypergeometric functions / closed forms (?) \\
But John says use beta fns instead - logs of gamma fns behave perfectly numerically \\
Method with computational advantage should win out \\

\item Read Maruyama and George (2011)
\end{enumerate}

Regress $x_{ij} = \sum_{k \ne j} \vbeta_k x_{ik} + \epsilon_{ij}$ to fit network

John cautioned that we may run into the following problem: if two covariates $x_1$ and $x_2$ have
no relationship i.e. $\text{cor}(x_1, x_2) = 0$, as graphically depicted below

\begin{tikzpicture}
\draw[->] (0, -1) -- (0, 4);
\draw[->] (-1, 0) -- (4, 0);
\node [above] at (0, 4) {$x_2$};
\node [below] at (4, 0) {$x_1$};
\draw [ultra thick] (-1, 0) -- (3.5, 0);
\foreach \x in {0, ..., 3}
	{\draw[fill, red] (\x - .5, 0) circle [radius=2pt];}
\end{tikzpicture}

then when the roles of $x_1$ and $x_2$ are interchanged

\begin{tikzpicture}
\draw[->] (0, -1) -- (0, 4);
\draw[->] (-1, 0) -- (4, 0);
\node [above] at (0, 4) {$x_1$};
\node [below] at (4, 0) {$x_2$};
\draw [ultra thick] (0, -1) -- (0, 3.5);
\foreach \y in {0, ..., 3}
	{\draw[fill, red] (0, \y - .5) circle [radius=2pt];}
\end{tikzpicture}

the correlation will not exist, as $R^2 = \frac{\vy \mX (\mX^\top \mX)^{-1} \mX \vy}{\vy^\top \vy}$ and
$x_{i1} = 0$ for all $1 \leq i \leq n$. Hence, $(\mX^\top \mX)$ is singular, and the inverse does not exist.

John said that we should check for this case. Using the Singular Value Decomposition (SVD) helps, as it
downweights the eigenvalues of the $\mX^\top \mX$ matrix which are close to 0.

\section{To Do this week \ldots}
\begin{itemize}
\item Test that the \texttt{correlations.cpp} code matches the \texttt{Hitters.Rs} output
\item Implement code with a fixed and a varying component, as this helps John $\mC = [\mX, \mZ]$
\item VB approximation
\item Read literature, and re-read John's research grant application
\item Another paper in JCGS - posterior consistency, ugly expression
\end{itemize}

John requested that we re-schedule our next meeting until Thursday, as he has a research grant application
due next Wednesday.
\end{document}