\documentclass{article}[12pt]
\usepackage{amsmath}
\input{include.tex}
\input{Definitions.tex}
\title{Meeting notes - 9/3/2015}
\begin{document}

\maketitle

I updated John on my progress with the zero-inflated Poisson mixed model with random
intercepts and slopes. For my test case, all algorithms currently work well except GVA with
$\mLambda = (\mR^T\mR)^{-1}$. The algorithm does not perform as well as the others, getting
poor accuracy, as little as $33\%$ for the fixed effects.

John mentioned that either parameterisation (meaning $\mLambda=\mR^T \mR$ or 
$\mLambda=(\mR^T \mR)^{-1})$) span space of semi-definite matrices, but when optimising the 
GVA lower bound they may have different local optima.

He suggested a number of possible next steps.

\begin{itemize}
\item Look at different starting points.

\item Sensitivity analysis
\begin{enumerate}
\item[a] $\vr = \vone_n$.
\item[b] Fit Poisson mixed model using only $y > 0$ data.
\item[c] Predict $\vr$ from (a)
\item[d] Random $\vr$ - see sensitivity - $\vr = \vone$, $y > 0$.
$\vr$ random $y=0$ with problem $\half$ or prob of $0$.
\item[e] $r=1$ for $y > 0$, $\vr=\vzero$ for $y=0$.
\end{enumerate}

\item John suggest I do the same for the Laplace's method of approximation approach.

\item Mixture models. Use k means to start centres.

\item Look at $\vmu$. Check that this is being estimated correctly. (Update: I've since
done this, and it is).

\item blocksize 4 or 5 dimensional, higher dimensional quadrature type methods
MCEM.

\item I said I wanted to review my vector calculus and matrix calculus. John said he'd
already asked me to do this. I responded that I had, but that I understood my problem
much better now.
\end{itemize}

\end{document}