\documentclass{amsart}
\title{Meeting with Dr John Ormerod - 08/01/2016}

\input{Definitions.tex}

\begin{document}

\maketitle

$R^2 = \frac{\vy^\top \mX (\mX^top \mX)^{-1} \mX^\top \vy}{\vy^\top \vy}$

$\hat{\vy} = \mH \vy$

$q = 20 - 30$
|Model space| $\approx 2^30, 10^9$

C++ $10^5$ models/second per core

$\mX$ fixed
$\mZ$ All combinations

Prototype R code

$R^2 = \frac{\vy^\top [\mX \mZ_\gamma]
\begin{pmatrix}
\mX^\top \mX & \mX^\top \mZ_\gamma \\
\mZ_\gamma ^\top \mX & \mZ_\gamma^\top \mZ_\gamma
\end{pmatrix}^{-1}
\begin{bmatrix}
\mX^\top \vy \\
\mZ_\gamma^\top \vy
\end{bmatrix}}{\vy^\top \vy}
$

Gray code for $\gamma$, other alternatives
CPU/GPU
CVB.fast

Keep working on definitions
CSDA
Collapsed Variational Bayes

$\gamma \to \mA \text{ row of $\mA$, same number of columns as $\mZ$}$

Null model contains $\mX$ only

Eventually, network models
$\gamma \in \bR^p$, search strategy, first model toggle first element, second model toggle second element etc.

Ask Jean for HPC

Good prognosis and bad prognosis - QDA classifier
Using DLDA now, assumes $\mSigma$ diagonal, unlikely to be true in practice.


Stepwise constant survival function, incomplete gamma functions.
Linear model - closed form.
Piecewise constant hazard models have closed forms for their marginal likelihoods - or so John believes.
VB over some indicators.
Then VB over the gammas.

$$
\vy_i =
\begin{cases}
1 & \text{poor prognosis group} \\
0 & \text{good prognosis group} \\
\text{unobserved} & \text{for the middle group}
\end{cases}
$$

LDA - fitting two normals.

Differential distribution? Ask Dario, ask John again.
Skew normals? Didn't help with Dario's problem, as $n=47$, kernel density estimation i.e. non-parametric with
a high number of parameters.
Asymptotics $O(n^{-1/5}$ for KDE nonparametrics, $O(n^{-1/2}$ for parametric estimators.
Model averaging.
Lass, Hastie, add to Mendeley. glasso, sparse PCA, sparse CCA.
Lasso is a straw man, everyone beats it, something to compete against.

John will send me the presentation with th details of the rank 1 updates, and his grant proposal when it's
finished.
I should do the third assignment from John's Bayesian course, to master the relevant algebra.

24 hours, GLASSO, $p=10^6$, 30 cores
semidefinite programming
QIC CRAN
Big \& QUIC multicore version, unreleased, source code released to us

Paper 2: CVB for linear models.
Paper 3: Networks, differential networks, sparse QDA.

\end{document}