\documentclass{article}[12pt]
\usepackage{amsmath}
\input{include.tex}
\input{Definitions.tex}
\title{Meeting notes - 13/4/2015}

\begin{document}
Laplace's Method and NR can be unstable. John discussed that other research
groups had not found the NR style algorithms to be unstable. I mentioned that I
could easily come up with examples that wouldn't converge using Laplace's Method
or NR.

I discussed with John that the inverse parameterisation algorithm can get stuck
in a bad part of the parameter space if it's initialised poorly. The current fix
I'm using is to run GVA with the $\mR \mR^T$ parameterisation for two
iterations, then switch to the Laplace's Method/$(\mR \mR^T)^{-1}$ algorithm.
This is still faster than the previous algorithm.

John and I agreed that the performance problems in the code are essentially
solved or can be easily solved, and that it's time to move on. We should
concentrate on splines now.

John talked about the various kinds of splines, including B splines and
O'Sullivan splines.

John suggested I review Challis's papers on alternative parameterisations
for variational approximations.

Diagnostic $x_i^T (\mX^T \mW \mX + D)^{-1} x_i$ high $to$ high influence.

We discussed applying the approximation to the physical activity data
from Panorg. John asked whether I had permission to use the data. I said
that I was still on good terms with the Panorg staff, and would be able to
talk to them and get permission to use the data.

John also mentioned that we need to be careful about overflow and underflow.
The principal issue is the weighting matrix $\vw = \exp{\mX \vmu}$. If $\vmu$
becomes even moderately large, then $\vw$ can diverge.
\end{document}