\documentclass{beamer}

\usetheme{Warsaw}
\usepackage{graphicx}
\usepackage{ulem}
\usepackage{tikz}
\usepackage{listings}
\input{include.tex}
\input{Definitions.tex}

\usefonttheme{serif}

\title{Progress update}
\author{Mark Greenaway}

\mode<presentation>
{ \usetheme{boxes} }

\begin{document}
\begin{frame}
\titlepage
\end{frame}

\begin{frame}{How to be impactful, and packaging my code}
\begin{itemize}
\item JSM 2016 was on last week.
\item Skipper Seabold gave a talk called ``Having an Impact as a Modern Statistician'' \url{https://speakerdeck.com/jseabold/having-an-impact-as-a-modern-statistician}.
\item So I was thinking ``How can I be more impactful?''.
\item John also asked me last week for the latest version of my correlation code.
\item So I thought ``I know, I'll put it in an R package''! Because the only impactful code is code people can
actually use.
\item That means it needs to build and run everywhere.
\item I'm fixing some build problems on Windows. I hope to have the package ready by next week.
\item I'm finding the \texttt{Rcpp} and \texttt{devtools} packages really helpful.
\item I've been reading ``Writing R Extensions'', which has information you can't find anywhere else.
\end{itemize}
\end{frame}

\begin{frame}{Other stuff}
\begin{itemize}
\item Abstract submitted to ASC 2016 before the deadline. Which they've since extended.
\item Andrew Stefan got a job at Boeing. He's leaving at the end of the month. So we'll have a lot more
research server capacity.
\item Checking through algebra that John gave me to look at, which will allow us to update the determinants
of $\mX_\vgamma^\top \mX_\vgamma$ at the same time as we update $(\mX_\vgamma^\top \mX_\vgamma)^{-1}$.
\item This is all based on the block inverse formula, which I now understand.
\item No errors yet, touch wood. But I'm only a third of the way down the page he gave me. I got stuck after
that.
\item Writing, writing, writing \ldots.
\end{itemize}
\end{frame}

\end{document}