\documentclass{beamer}

\usetheme{Warsaw}
\usepackage{graphicx}
\usepackage{ulem}
\usepackage{tikz}
\input{include.tex}
\input{Definitions.tex}

\usefonttheme{serif}

\title{Progress update}
\author{Mark Greenaway\\PhD candidate\\markg@maths.usyd.edu.au}

\mode<presentation>
{ \usetheme{boxes} }

\begin{document}
\begin{frame}
\titlepage
\end{frame}

\begin{frame}{TopServeR}
\begin{itemize}
\item Last week I was talking about getting access to more computers.
\item Then I thought \ldots we have lots of computers. We're just not fully leveraging them.
\item Question for discussion: why is that? There's an IT Committee meeting coming up, where we can discuss
			any ongoing issues.
\item There's a web page Paul Szabo provides called topserver: \url{http://www.maths.usyd.edu.au/ub/psz/loc/topserver}
\item To make things easier for myself and others, I wrote some R code to query this: \url{https://github.com/certifiedwaif/topserveR}
\item Example usage:
\tiny
\begin{verbatim}
> source("topserveR.R")\\
> topserver()
\end{verbatim}
\begin{tabular}{l}
 [1] "anaona: Idle time 61.04\% on 40 CPUs over  52.78 days; load 2.05 3/345 14728"   \\
 [2] "anbona: Idle time 30.09\% on 40 CPUs over  52.78 days; load 50.00 51/430 29895" \\
 [3] "ancona: Idle time 85.98\% on 40 CPUs over  52.78 days; load 2.07 3/352 11143"   \\
 [4] "andona: Idle time 46.86\% on 40 CPUs over  52.78 days; load 40.07 41/369 6075"  \\
 [5] "bivona: Idle time 89.83\% on 32 CPUs over  52.78 days; load 0.05 1/278 26069"   \\
 [6] "briona: Idle time 99.51\% on 24 CPUs over  52.78 days; load 0.05 1/230 11857"   \\
 [7] "cetona: Idle time 98.84\% on  8 CPUs over  21.18 days; load 0.05 1/130 31726"   \\
 [8] "esaona: Idle time 37.47\% on 32 CPUs over  52.78 days; load 32.11 33/326 15939" \\
 [9] "esbona: Idle time 85.73\% on 32 CPUs over  52.78 days; load 0.05 1/313 31753"   \\
[10] "escona: Idle time 84.79\% on 32 CPUs over  52.78 days; load 0.05 1/290 27626"   \\
[11] "esdona: Idle time 54.08\% on 32 CPUs over  52.78 days; load 32.13 33/327 7840"  \\
[12] "gemona: Idle time100.00\% on 24 CPUs over  52.78 days; load 0.05 1/230 14208"   \\
[13] "oraona: Idle time 83.99\% on 32 CPUs over  52.78 days; load 14.60 14/702 15421" \\
[14] "orbona: Idle time 84.47\% on 32 CPUs over  52.78 days; load 17.31 15/871 6256"  \\
[15] "orcona: Idle time 87.05\% on 32 CPUs over  52.78 days; load 14.53 14/701 19117" \\
[16] "ordona: Idle time 88.29\% on 32 CPUs over  52.78 days; load 14.49 14/702 28129" \\
[17] "ossona: Idle time 99.61\% on  8 CPUs over  52.78 days; load 0.05 1/130 9903"    \\
[18] "parona: Idle time 99.82\% on  8 CPUs over  52.78 days; load 0.05 1/130 10026"   \\
[19] "savona: Idle time 39.40\% on 32 CPUs over  52.78 days; load 15.97 5/1132 13169" \\
[20] "verona: Idle time 59.92\% on 48 CPUs over  52.79 days; load 24.56 26/775 12182" \\
\end{tabular}
\end{itemize}
\end{frame}

\begin{frame}{Progress last week}
\begin{itemize}
\item Substantial progress on the Variational Bayes Mean field updates for the linear model selection model.
\item Numerical issues with evaluating the mean field update for $g$
\item Many more papers read and understood.
\item The correlations code could be faster: use $\mX^\top \mX$ to look up products of $\mX_\gamma^\top \vx$
rather than re-calculating them. This requires yet another partial re-write, but the result will be well worth
it - five times faster \emph{at least}
\item The benchmark is 300,000 or a little above $2^{18}$ models a second on one core. We think we can do better than that
\item Multiply that out by the number of cores in the school plus HPC \ldots that's a lot of models
\end{itemize}
\end{frame}

\end{document}