\documentclass{beamer}

\usetheme{Warsaw}
\usepackage{graphicx}
\usepackage{ulem}
\input{include.tex}
\input{Definitions.tex}

\usefonttheme{serif}

\title{Progress report - 18/01/2016}
\author{Mark Greenaway\\PhD candidate\\markg@maths.usyd.edu.au}

\mode<presentation>
{ \usetheme{boxes} }

\begin{document}
\begin{frame}
\maketitle
\end{frame}

\begin{frame}{Third year -- time crunch}
\begin{itemize}
\item John used to think I was incompetent.
\item Now he just thinks I'm lazy.
\item That's \emph{progress}! Now I just need to be less lazy \ldots
\item I'm good at computers, and okay at mathematical statistics. I need to get better at mathematical statistics.
\item Six months to do the work for the second paper.
\item Begin third paper.
\item Write thesis.
\item OMG.
\item OMFG.
\end{itemize}
\end{frame}

\begin{frame}{Work at the right level -- Computational Statistics}

\begin{itemize}
\item With time running out, I have to alter my strategy.
\item The problems that we work on are motivated by mathematical and statistical concerns.
\item Computers are a means to an end.

\item \begin{enumerate}
\item Statisticians / applied mathematicians.
\item Numerical analysts.
\item Computer scientists.
\end{enumerate}

\item It's fine for everyone to work at level one, and for people like John or
myself to work at level two. 
\item We shouldn't spend too much time at level
three. We should let computer scientists do their jobs, and we should do ours.

\end{itemize}
\end{frame}

\begin{frame}{R and C++}
\begin{itemize}
\item I'm getting much better at writing C++, and integrating C++ with R.
\item That's good, because R is hard to optimise.
			\begin{quote}
			``The only way to reliably speed up R code is to re-write it in another language.'' - John D. Cook
			\end{quote}
\item People typically design their numerical algorithms to minimise the number of floating point operations. 
	  	They should also pay attention to how memory is used.
\item Good numerical linear algebra textbooks e.g. Numerical Linear Algebra by Trefethen and Bau make this
			point early and forcefully.
\item I'm using the Eigen library for linear algebra.
\item I'm in good company. Douglas Bates (lme4) and Dirk Eddelbuettel (Rcpp) recommend this approach in
			``Fast and Elegant Numerical Linear Algebra Using the RcppEigen Package''.
\end{itemize}
\end{frame}

\begin{frame}{R and C++: Parallelisation}
\begin{itemize}
\item Make it run. Make it right. Make it fast. Always in that order.
\item CPUs single core first, then multi core, then GPUs.
\item For technical reasons, I don't think R's parallelisation i.e. \texttt{mclapply()} and friends is ideal,
			although I'm open to being convinced otherwise.
\item OpenMP/RcppParallel for multi core parallelisation.
\item Andrew Stefan has been helping me learn how to use OpenMP for multi core.
\item Florian has been helping me begin to understand GPUs.
\item Everything will be released in an R package that runs on all platforms and that everyone can use.
\end{itemize}
\end{frame}

\begin{frame}{Correlation}

\begin{itemize}
\item Let $\vgamma$ be the vector of indicators in $\R^p$. Then

\begin{equation*}
R^2_\vgamma = \frac{\vy^\top [\mX \mZ_\gamma]
\begin{pmatrix}
\mX^\top \mX & \mX^\top \mZ_\gamma \\
\mZ_\gamma ^\top \mX & \mZ_\gamma^\top \mZ_\gamma
\end{pmatrix}^{-1}
\begin{bmatrix}
\mX^\top \vy \\
\mZ_\gamma^\top \vy
\end{bmatrix}}{\vy^\top \vy}
\end{equation*}

\item I have C++ that can fit 50,000 models per second on a single core, doing $O(p^3)$ inversions. 
\item Rank one updates and downdates allow us to update the inverse in the above expression in $O(p^2)$.
\item $O(p^3) \to O(p^2)$ is a $p$-fold speedup. For large $p$, this is a massive win.
\item The model fits are all independent of one another, so with $m$ cores, I should theoretically be able
			to get a further $m$-fold speed-up.
\end{itemize}
\end{frame}

\begin{frame}{Windows}
\begin{itemize}
\item I own a PC now.
\item I decided to stop being an operating system hipster and try Windows 10.
\item *cough* It's not that bad. *cough*
\item Mmmm, this humble pie is delicious \ldots
\end{itemize}
\end{frame}

\end{document}
