\documentclass{beamer}

\usetheme{Warsaw}
\usepackage{graphicx}
\usepackage{ulem}
\input{include.tex}
\input{Definitions.tex}

\usefonttheme{serif}

\title{Progress update}
\author{Mark Greenaway\\PhD candidate\\markg@maths.usyd.edu.au}

\mode<presentation>
{ \usetheme{boxes} }

\begin{document}
\begin{frame}
\titlepage
\end{frame}

\begin{frame}{Project plan}
\begin{itemize}
\item We're aiming to submit our second paper by July. \\
\item This is an aggressive timeframe, but I think an achievable one. \\
\item Writing a paper is a project. Standard project planning techniques will work. \\
\item John and I have drawn up a preliminary list of tasks, which we will continue to refine. \\
\item I much prefer working this way, because I know how to apportion my time, what's still left to do and what's on the horizon. \\ 
\item Getting Things Done (GTD) works for me. \\
\item Triage, triage, triage \ldots no GPUS at this stage. \\
\item If things go well, there's some interesting things to do in John's research grant
\end{itemize}
\end{frame}

\begin{frame}{Play to our strengths \ldots}
\emph{What are my strengths?}
\begin{itemize}
\item Degree in Computer Science (HD average in CS subjects) from 1995-1997, back when compiled languages like C and manual memory management was the norm. Code optimisation was a required skill.
\item A decade of software engineering experience. A book written on C++. Sadly, out of print \ldots
\item UNIX upbringing. Black belt in search and replace/text editor tricks. If it takes more than three keystrokes you're working too hard. Automate all the things!
\item Tech industry way of working - GitHub, Slack, Trello.
\item Pure mathematical upbringing - pedantry in the service of good.
\item Applied statistical experience - an idea of what's actually useful to applied statisticians in the field, with a public health focus.
\end{itemize}
\end{frame}

\begin{frame}{Writing and algebra}
\begin{itemize}
\item Writing \\
John shared this lovely poem with me. In honour of Valentine's Day yesterday, I'm sharing it with you too.
\begin{quote}
Roses are red. \\
Violets are blue. \\
I should be writing \\
And so should you. \\
\end{quote} \\
And they say romance is dead \ldots
\item Algebra \\
Deriving the VB approximation for the linear model with model selection. \\
Collapsed Variational Bayes.
\end{itemize}
\end{frame}

\begin{frame}{Major achievement of the last two weeks: correlations calculated by iterative updates}
\begin{itemize}
\item I work faster in C++, mostly due to the static typing / type checking. This alone is worth the price of 
			admission for me.
\item The C++ ecosystem has other advantages for a person like me: excellent numerical linear algebra 
			and other libraries, HPC, optimising vectorising compilers, build systems, debuggers, profilers.
\item Once John and I were on the same page with using the block inverse approach, we were able to go from 
			idea to working implementation in 10 days.
\item For a representative test case, our results match those produced by R to 4 decimal places. It might be 
			more, but I haven't changed the formatting of the results to check yet.
\end{itemize}
\end{frame}

\begin{frame}{Testing -- there's always room for improvement.}

\begin{itemize}
\item John admonished me for my somewhat slapdash black box testing.
\item Paraphrasing John: ``If the results of your program aren't numerically accurate, they're worthless.''
\item Together, we drew up a test plan. I thought I was staunch about testing, but it turns out that John is
\emph{even more} staunch. This is a good lesson for me to learn.
\item Test data based on the well-known Anscombe's quartet data set.
\item Refactored rank one update and downdate code into functions which we could test individually.
\item These functions will allow us to write the other programs we need to write much more quickly!
\end{itemize}
\end{frame}

\begin{frame}{What's next: coding?}
\begin{itemize}
\item Next step: more testing, unit tests, automated regression testing, test-driven development. No 
			back--sliding!
\item Hadley Wickham wrote a package for unit testing, called \texttt{testthat}.
\item Write other programs we need, for partitioned model selection etc.
\item Once the code is correct, optimise if necessary.
\item Parallelise using OpenMP.
\item Code to calculate the dependency matrix $D_{ij}$.
\item MCMC. Stan's not going to work, because of the discrete random variables involved. So we're going to 
			have to code it ourselves.
\end{itemize}
\end{frame}

\end{document}