\documentclass{beamer}

\usetheme{Warsaw}
\usepackage{graphicx}
\usepackage{ulem}
\input{include.tex}
\input{Definitions.tex}

\usefonttheme{serif}

\title{Progress update}
\author{Mark Greenaway\\PhD candidate\\markg\@maths.usyd.edu.au}

\mode<presentation>
{ \usetheme{boxes} }

\begin{document}
\begin{frame}
\titlepage
\end{frame}

\begin{frame}{Knuckling down \ldots}
\begin{itemize}
\item Focus: Clearing the decks. This year is about my PhD, and my brother.
\item No time for part-time work, except maybe tutoring. Got part-time job offers from CBA, IAG and interest
			from Phastar. Politely rejected them all, no time!
\item Mathematical statistics + Working code + Writing = Progress on my PhD
\item I need to be working on all of these things, at the same time
\item With a laptop and a smartphone, you can work anywhere!
\item Show visible progress on your PhD every week. Preferably every day
\item Zero-inflated model fitting code is now packaged as \texttt{zipvb}. Will be up on GitHub when the
			first paper is published
\end{itemize}
\end{frame}

\begin{frame}{Tools I'm using}
\begin{itemize}
\item \begin{tabular}{|l|l|p{3cm}|}
\hline
Tool & URL & Description \\
\hline
GitHub & \url{http://github.com} & Distributed version control \\
Slack & \url{http://slack.com} & Work-oriented chat \\
Trello & \url{http://trello.com} & Task list\\
Mendeley & \url{http://mendeley.com} & Citation manager
\hline
\end{tabular}
\item These tools are all multi-user, and integrate with one another. Happy to demonstrate them to you, but
			not now
\item They also help me account for my \emph{time}, and show progress immediately
\item I also use a text editor, because I work with a lot of code. I like Sublime Text (\url{http://www.sublimetext.com/})
\item If you're happy with RStudio, just use that. Or a text editor \emph{and} RStudio
\end{itemize}
\end{frame}

\begin{frame}{Block inverse formula}
% Copy from meeting notes
% Re-writing meeting notes to use in the paper and thesis
% Discarded old code, writing better, cleaner code
Let $\mA$ be a matrix partitioned into blocks,

\small
\begin{equation*}
\mA = \begin{pmatrix}
\mP & \mQ \\
\mR & \mS
\end{pmatrix}.
\end{equation*}
\normalsize

Then $\mA^{-1}$ is

\small
\begin{equation*}
\begin{pmatrix}
\mP^{-1} + (\mP^{-1}.\mQ).(\mS - \mR.\mP^{-1}.\mQ)^{-1}.(\mR.\mP^{-1}) & -(\mP^{-1}.\mQ).(\mS - \mR.\mP^{-1}.\mQ)^{-1} \\
-(\mS - \mR.\mP^{-1}.\mQ)^{-1}.(\mR.\mP^{-1}) & (\mS - \mR.\mP{^{-1}.\mQ}))^{-1}
\end{pmatrix}
\end{equation*}
\normalsize

If $\mS$ is a scalar, then the inversions involving $\mS$ become divisions.

Thus if the inverse of $\mP$, $\mP^{-1}$ is available, we can calculate the inverse of $\mA$ using matrix
multiplications in $O(p^2)$ time rather than $O(p^3)$, saving us a factor of $p$.

\end{frame}

\begin{frame}{Model selection correlations code}
\begin{itemize}
\item Writing correlation code in C++ using Eigen for linear algebra and Boost for bitstrings. 117
			lines of code so far.
			\url{https://github.com/certifiedwaif/phd/blob/master/code/correlation.cpp#L194-L311}
\item How to write numerical software (compiled language version) 
\begin{enumerate}
\item Make it build
\item Make it run
\item Make it right (testing)
\item Make it fast
\end{enumerate}
\item We're at Stage 2 right now. Initialisation works
\item Rank 1 update and downdate works a couple of times
\item Up to 5 iterations as of last week. About a million to go \ldots
\item I have a tricky state bug, which I hope to track down early this week
\end{itemize}
\end{frame}

\begin{frame}{Hadley Wickham is coming to town!}
\begin{itemize}
\item Well, Melbourne.
\item Close enough, right?
\item Book now, to avoid disappointment. Places are going fast.
\item \url{http://www.meetup.com/Data-Science-Melbourne/events/227234228/}
\item I'm going.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Functional programming comes to the Hadleyverse \ldots}
\begin{itemize}
\item The R programming community is part of the wider programming community, whether you choose to
			acknowledge this fact or not
\item Over the past few years, there has been an explosion of interest in functional programming in the wider
			programming community
\item Hadley Wickham started a GitHub project for monads last week (\url{https://github.com/hadley/monads})
\item We already have pipes in magrittr (\url{https://github.com/smbache/magrittr})
\item These libraries make R more like Haskell
\end{itemize}
\end{frame}

\end{document}