\documentclass{beamer}

\usetheme{Warsaw}
\usepackage{graphicx}
\usepackage{ulem}
\input{include.tex}
\input{Definitions.tex}

\usefonttheme{serif}

\title{Progress update - 16/05/2016}
\author{Mark Greenaway}

\mode<presentation>
{ \usetheme{boxes} }

\begin{document}
\begin{frame}
\titlepage
\end{frame}

\begin{frame}{Reading/Writing/Thinking}
\begin{itemize}
\item I've been mostly focusing on reading papers and writing. The phrase ``Shut up and write!''
			has entered my lexicon.
\item I now feel that writing should come before coding, because you can't write a program about something you 
			don't	understand.
\item Modelling my writing on John's thesis chapter, Ormerod and Wand 2010 and Liang et al. 2008.
\item My Mendeley is getting a workout.
\end{itemize}

\end{frame}

\begin{frame}{Model selection using Structured Variational Bayes}

We're going to do model selection using Structured VB.

Let $\underline{p}(.)$ denote the lower bound. Then

\begin{align*}
\underline{p}(\vy) &= \sum_\vgamma \underline{p}(\vy|\vgamma) p(\vgamma) \\
p(\vgamma|\vy) &\approx \frac{\underline{p}(\vy | \vgamma) p(\vy)}{\underline{p}(\vy)} \\
p(\vbeta|\vy) &\approx \sum_{\vgamma} q(\beta | \vy) p(\vgamma | \vy) \\
\end{align*}

\textbf{Idea:} We don't have to calculate these sums in strict order of the bit strings $\vgamma$. We could
visit them randomly. How quickly would they converge to the optimal answer? Stochastic Structured Variational
Bayes?

The only downside is that if we did this, we couldn't use rank one updates to calculate the correlations.

\end{frame}

\end{document}