\documentclass{beamer}

\usetheme{Warsaw}
\usepackage{graphicx}
\usepackage{ulem}
\input{include.tex}
\input{Definitions.tex}

\usefonttheme{serif}

\title{Progress report - 16/11/2015}
\author{Mark Greenaway\\PhD candidate\\markg@maths.usyd.edu.au}

\mode<presentation>
{ \usetheme{boxes} }

\begin{document}
\begin{frame}
	\maketitle
\end{frame}

\begin{frame}{What I've been up to}
	\begin{itemize}
		\item Integral for the exact posterior $p(\vbeta|\vy)$
		\item More integrals for checking John's calculations for the variational approximation
		\item Marking assignments and exams
	\end{itemize}
\end{frame}


\begin{frame}{Integral for the exact posterior $p(\vbeta|\vy)$}
	\begin{itemize}
		\item Numeric integration is often computationally expensive, and an analytic solution is preferable.
		\item I tried using the substition $h=\frac{g}{1 + g}$, using geometric series for $\frac{1}{1 + g}$
					and using a Taylor series expansion for $\frac{g}{1 + g}$. Unfortunately, these didn't help me
					to do the integral.
		\item I discovered Computer Algebra Systems. In particular, I discovered Sage, based on python, and
					Mathematica. That was a lot of fun, and I'm sure I'll use those more in the future.
		\item But Mathematica couldn't do the integral either. So it's back to the drawing board -- maybe John
					and I can combine our ideas?
		\item I'm open to any suggestion -- numeric approaches, approximations, weird integrals I've never even
					heard of etc.
	\end{itemize}
\end{frame}


\begin{frame}{More integrals for checking John's calculations for the variational approximation}
	\begin{itemize}
		\item All the practice I got trying to do the previous integral really helped with these integrals
		\item So far, everything checks out for $p(y)$, $p(g|y)$, $p(sigma2|y, g)$
		\item I should get through the rest of the integrals in the next few days
	\end{itemize}
\end{frame}

\begin{frame}{Marking}
	\begin{itemize}
		\item I'm snowed under with marking for the next couple of weeks, but it's coming to an end
		\item STAT3011 computer practical exam for Ray
		\item STAT3012 exam marking for Samuel
		\item MATH3076/MATH3976 marking for Sheehan, although I think I can hand that over to Matt
		\item I'm getting mild RSI, so will try to do more work on paper this week
	\end{itemize}
\end{frame}

\end{document}
