\section{Introduction}

Start off with a summary of the Particle Em for Variable Selection paper by Veronika Rockova

Introduction
EM vulnerable to local entrapment when likelihood is multi-modal, especially spike-and-slab posterior
distributions for model selection
non-parametric Variational Bayes, repulsive particles. These particles are geared towards unchartered areas of
the posterior, providing a more comprehensive summary of its' topography than simple parallel EM deployments
Report of a single model will be a misleading reflection of the model uncertainty in a highly multimodal
posterior. Identify a collection of representative models
What's our choice of prior?
Hard to explore model space and escape local entrapment, especially in high dimensions
Population-based methods, allow trajectories to ``communicate''

Main contributions
As a precursor to Particle Em, we propose the Reversed EMVS algorithm, a discrete optimisation approach for
spike-and-slab variable selection. Treat $\vgamma$ as parameters of interest, and $\vbeta$ as missing data.
Closed form updates, targeting the discrete model space.

Population-based optimisation approach that exhibits both individual and social behaviour. Particles share a
common goal (finding essential posterior modes) and realise it by exploring the posterior environment while
mutually interacting. Social behaviour is mediated through entropy, which serves as a diversifying penalty.

Entire trajectory of evolving posteriors is far more informative for variable selection

By forging connections between Particle EM and sequential Monte Carlo (SMC) procedures, we propose a
stochastic Particle EM variant

Visualisation

Approximate Bayesian inference
Variational Approximation
Variational Bayes
Collapsed Variational Bayes
