\documentclass{beamer}

\usetheme{Warsaw}
\usepackage{graphicx}
\usepackage{ulem}
\input{include.tex}
\input{Definitions.tex}

\usefonttheme{serif}

\title{Progress report - 18/01/2016}
\author{Mark Greenaway\\PhD candidate\\markg@maths.usyd.edu.au}

\mode<presentation>
{ \usetheme{boxes} }

\begin{document}
\begin{frame}
\maketitle
\end{frame}

\begin{frame}{No C++ is best C++ ...}
\begin{itemize}
\item We're R programmers. The best pay-off for effort spent is to speed up R code
\item If we solve speed problems by using C++, I'm the ``only'' person who can do that and that makes me
			the bottleneck. Not very smart from a project management point of view
\item Let's look at this web page: http://www.statsblogs.com/2016/01/21/parallel-blas-in-r/
\item Conclusion: Don't use reference BLAS if something better is available. You're wasting time
			\emph{unnecessarily}
\item If you need help, ask me. If my supervisor says it's okay, I'll upgrade your R installation myself.
\end{itemize}
\end{frame}

\begin{frame}{Tools I like, and would recommend}
\begin{itemize}
\item Sublime Text - my favorite text editor of all time. For people who like need to see more code.
\item Trello - multi-user to do lists
\item Slack - Like Facebook chat for people with work to do
\item GitHub
\item All of these tools integrate with each other
\item Twitter/IRC - Useful social media
\end{itemize}
\end{frame}

\begin{frame}{Progress in the past week or two}
\begin{itemize}
\item Not as much as I'd like. Life took a dramatic turn
\item Drama is quite tedious actually. It stops you from doing things. I've moved in with my brother, and
			the focus is on drama minimisation
\item Zero-inflated model code is now packaged - zipvb
\item Progress on rank-one updates and downdates, and a black belt in Sherman-Woodbury
\begin{equation*}
(\mA + \vu \otimes \vv)^{-1} = \mA^{-1} - \frac{(\mA^{-1} . \vu) \otimes (\vv . \mA^{-1})}{1 + \lambda}
\end{equation*}
where $\lambda = \vv . \mA^{-1} . \vu$ and $(\vu \otimes \vv)_{ij} = \vu_i \vv_j$
\item But I'd like to talk to John about this. There are many approaches, and this might not be the best
\end{itemize}
\end{frame}

\end{document}
