\documentclass{beamer}

\usetheme{Warsaw}
\usepackage{graphicx}
\usepackage{ulem}
\input{include.tex}
\input{Definitions.tex}

\usefonttheme{serif}

\title{Progress report - 9/2/2015}
\author{Mark Greenaway\\PhD candidate\\markg@maths.usyd.edu.au}

\mode<presentation>
{ \usetheme{boxes} }

\begin{document}
\begin{frame}
\maketitle
\end{frame}

\begin{frame}{Work on converting Inverse Gamma prior to Inverse Wishart prior}

Inverse Gamma $$\frac{\beta^\alpha}{\Gamma{(\alpha)}} x^{-\alpha-1} \exp{\left(\frac{-\beta}{x}\right)}$$

Inverse Wishart $$
\frac{|\Psi|}{2^{\frac{vp}{2}} \Gamma_p {(\frac{v}{2})}} |\mX|^{\frac{v + p + 1}{2}}
\exp{\left(- \half \tr{(\Psi \mX^{-1})} \right)}
$$

\begin{tabular}{l|c}
Tasks & Done \\
\hline
Mean field update & $\text{\rlap{$\checkmark$}}\square$ \\
Gaussian & $\text{\rlap{$\checkmark$}}\square$ \\
MCMC & $\text{\rlap{$\checkmark$}}\square$ \\
Accuracy & $\square$ \\
\end{tabular}
\end{frame}

\begin{frame}{MCMC speed - time to run 1,000 iterations}

The MCMC was coded in Stan.

\begin{tabular}{c|rrr}
Run & Burn-in & Sampling & Total \\
\hline
1 & 25.8481
& 112.561
& 138.409\\

2 & 143.456
& 275.616
& 419.072\\

3 & 190.31&
290.188&
480.498\\

4 &  194.666
& 296.524
& 491.19\\
\end{tabular}

Initial indications are that this is going to take a lot of computer time when I want
to run 1,000,000 iterations.

To save time, I save the results of my MCMC in an RData file, and re-load it to perform
accuracy calculations.
\end{frame}

\begin{frame}[fragile]{Why is the MCMC so slow?}
It might be because of the way I've coded the Stan file:
\begin{verbatim}
vector[B] u[M];
...
for (n in 1:N) {    
    eta <- dot_product(X[n], vbeta);
    for (m in 1:M)
      for (b in 1:B)
        eta <- eta + Z[n,(m-1)*B+b]*u[m][b];
\end{verbatim}

Triple-nested hand-coded loops are generally not very fast. Stan is written using
the popular Eigen library, which uses SIMD instructions to speed up calculations where 
possible e.g. \texttt{dot\_product} is fast.

There's probably a better way to code this in Stan. But this might be a case of 
diminishing returns.

\end{frame}

\begin{frame}{Future work}
\begin{itemize}
\item Finish conversion to Inverse Wishart, and re-run accuracy checks. The accuracy
results are currently quite weird, and I don't believe them
\item There is support for splines, but it is currently broken and needs to be fixed
and checked for accuracy
\item Revise results in draft paper
\item The code is becoming a bit of a mess
\end{itemize}
\end{frame}

\end{document}
