\documentclass{beamer}

\usetheme{Warsaw}
\usepackage{graphicx}
\usepackage{ulem}
\input{include.tex}
\input{Definitions.tex}

\usefonttheme{serif}

\title{Progress update}
\author{Mark Greenaway\\PhD candidate\\markg@maths.usyd.edu.au}

\mode<presentation>
{ \usetheme{boxes} }

\begin{document}
\begin{frame}
\titlepage
\end{frame}

\begin{frame}{Two week update}
\begin{itemize}
\item I'm not here early next week, as I'll be fan-boying at Hadley Wickham / taking a short sabbatical in 
			Melbourne. Back Tuesday or Wednesday.
\item Will most definitely still be working!
\item Will have my laptop and a fast net connection / be hanging out at Latrobe University with my friend and 
			fellow bioinformatics researcher Charles Gray.
\item Could Skype into the meeting, as Shila does.
\end{itemize}
\end{frame}

\begin{frame}{Project plan}
\begin{itemize}
\item We're aiming to submit our second paper by July. \\
\item This is an aggressive timeframe, but I think an achievable one. \\
\item Writing a paper is a project. Standard project planning techniques will work. \\
\item John and I have drawn up a preliminary list of tasks, which we will continue to refine and develop
			into a project plan. \\
\item I much prefer working this way, because I know how to apportion my time, what's left to do and 
			what's coming. \\ 
\item Getting Things Done (GTD) works for me. \\
\item Triage, triage, triage \ldots no GPUS at this stage. No time to pursue ``interesting'' tangents.\\
\item If things go well, there's an RA role mentioned in John's research grant. I \emph{want} that role.
			That's a beautiful carrot, which I'm chasing.
\end{itemize}
\end{frame}

\begin{frame}{Play to our strengths \ldots}
\emph{What are my strengths?}
\begin{itemize}
\item Degree in Computer Science (HD average in CS subjects) from 1995-1997, back when compiled languages 
			like C / Fortran and manual memory management was the norm.
\item Code optimisation was a required skill back then. I can translate a section of C code into the
			equivalent assembly language instructions in my head. I count clock cycles. I have a fair idea what your
			CPU's cache is doing. I actually \emph{enjoy} this sort of thing.
\item A decade of software engineering experience. A book published on C++. Sadly, out of print \ldots
\item UNIX upbringing. Text editor proficiency. If it takes more than three keystrokes you're working too 					hard. Automate all the things!
\item Tech industry way of working - GitHub, Slack, Trello.
\item Pure mathematical upbringing - pedantry is awesome!
\item Strong interest in numerical analysis, floating point representation and numerical linear algebra.
\end{itemize}
\end{frame}

\begin{frame}{Writing and algebra}
\begin{itemize}
\item Writing \\
John shared this lovely poem with me. In honour of Valentine's Day yesterday, I'm sharing it with you.
\begin{quote}
Roses are red. \\
Violets are blue. \\
You should be writing \\
And I should be too. \\
\end{quote} \\
And they say romance is dead \ldots \\
Not coincidentally, I did some writing over the weekend. \\
\item Algebra \\
Deriving the VB approximation for the linear model with model selection. \\
Collapsed Variational Bayes next.
\end{itemize}
\end{frame}

\begin{frame}{Major achievement of the last two weeks: correlations calculated by iterative updates}
\begin{itemize}
\item I work faster in C++, mostly due to the static typing / type checking. This alone is worth the price of 
			admission for me.
\item The C++ ecosystem has other advantages for a person like me: excellent numerical linear algebra 
			and other libraries, HPC, optimising vectorising compilers, build systems, debuggers, profilers.
\item Once John and I were on the same page with using the block inverse approach, we were able to go from 
			idea to working implementation in 10 days.
\item For a representative test case, our results match those produced by R to 4 decimal places. It might be 
			more, but I haven't changed the formatting of the results to check yet.
\end{itemize}
\end{frame}

\begin{frame}{Testing -- there's always room for improvement.}
\begin{itemize}
\item John admonished me for my somewhat slapdash black box testing. And he was 100\% right.
\item Paraphrasing John: ``If the results of your program aren't numerically accurate, they're worthless.''
\item A useful metaphor: who cares how fast you can run, if you're heading to the wrong place?
\item Together, we drew up a test plan. I thought I was staunch about testing, but it turns out that John is
\emph{even more} staunch. This is a good lesson for me to learn.
\item Test data based on the well-known Anscombe's quartet data set.
\item Refactored rank one update and downdate code into functions which we could test individually.
\item These functions will allow us to write the other programs we need to write much more quickly!
\end{itemize}
\end{frame}

\begin{frame}{What's next: coding?}
\begin{itemize}
\item Next step: more testing, unit tests, automated regression testing, test-driven development. No 
			back--sliding!
\item Hadley Wickham wrote a package for unit testing, called \texttt{testthat}.
\item Write other programs we need, for partitioned model selection etc.
\item Once the code is correct, optimise \emph{if necessary}.
\item Parallelise using OpenMP.
\item Code to calculate the dependency matrix $D_{ij}$.
\item MCMC. Stan's not going to work, because of the discrete random variables involved. So we're going to 
			have to code it ourselves.
\end{itemize}
\end{frame}

\end{document}