\documentclass{beamer}
\usepackage{beamerthemesplit}
\usepackage{color,xcolor,ucs}
\usetheme{Warsaw}
\usepackage{graphicx}
\usepackage{ulem}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usepackage{subcaption}
\usepackage{algorithm,algorithmic}
\usepackage{natbib}
\usepackage{cancel}
\input{../include.tex}
\input{../Definitions.tex}

\usefonttheme{serif}

\title{Exact expressions for parameter posteriors in Bayesian linear model selection}
\author{Mark Greenaway, Dr John Ormerod}

\mode<presentation>
{ \usetheme{boxes} }


\begin{document}
% Things we derived
\begin{frame}
	\frametitle{Calculating $p(\vy | \vgamma)$}
	We want to calculate $p(\vy | \vgamma)$ so that we can calculate $p(\vgamma | \vy)$ using Bayes' Rule and rank models against	one another. \\
	To do this, we need to calculate
	$$p(\vy | \vgamma) = \int p(\vy | \alpha, \vbeta, \sigma^2, \vgamma) p(\alpha) p(\vbeta | g, \vgamma) p(\sigma^2) p(g) d \alpha d \vbeta d \sigma^2 d g.$$
	We choose our priors so that this integral is tractable, with help from \cite{Gradshteyn1988}.
	The marginal likelihoods behave like BIC. \\
	We found the following closed form expressions.
	\small
	\begin{itemize}
		\item Liang et al. 2008 hyper-$g$ prior \cite{Liang2008}
			$p(\vy | \vgamma) = \frac{K(n) (a - 2)}{p_\vgamma + a  - 2} {}_2 F_1 \left( \frac{n-1}{2}, 1; \frac{p_\vgamma + a}{2}; R_\vgamma^2 \right)$
		\item Liang et al. 2008 hyper-$g/n$ prior \cite{Liang2008}
			$p(\vy | \vgamma) = \frac{K(n) (a - 2)}{n (p_\vgamma + a  - 2)} F_1 \left( 1, \frac{a}{2}, \frac{n-1}{2}; \frac{p_\vgamma + a}{2}; 1 - \frac{1}{n}, R_\vgamma^2 \right)$
	\end{itemize}
	These expressions are numerically stable to evaluate.
\end{frame}

\note{We want to be able to calculate the marginal likelihood of the data given $\vgamma$, so that we can
			calculate the posterior probability of $\vgamma$ and rank models against one another. To do this, we
			need to calculate the following integral.
			We choose our priors so that this integral is tractable, with help from the book Table of Integrals and
			Series by Gradshteyn. The marginal likelihoods behave like BIC.
			We found closed form expressions for the marginal likelihood for the hyper-$g$ and hyper-$g/n$ priors.}

\begin{frame}
	\frametitle{Calculating $p(\vy | \vgamma)$ for Bayarri's robust prior}
	\begin{itemize}
		\item Bayarri calculated the marginal likelihood given $\vgamma$ for the Robust Bayarri prior
		 	in \cite{Bayarri2012} 
			\tiny
			$p(\vy | \vgamma) = K(n) \left(\frac{n + 1}{1 + p_\vgamma}\right)^{-p_\vgamma/2} \frac{(1 - R^2_\vgamma)^{-(n-1)/2}}{p_\vgamma + 1} {}_2 F_1 \left[ \frac{n-1}{2}, \frac{p_\vgamma+1}{2}; \frac{p_\vgamma + 3}{2}; \frac{[1 - 1/(1 - R^2_\vgamma)](p_\vgamma + 1)}{1 + n} \right]$.
		\small
		\item But this expression is not numerically well-behaved, because the second argument of the
					${}_2 F_1$ function is greater than $1$.
		\item Using a trick that's available when ${}_2 F_1(., 1; .; .)$ ... is numerically
					well-behaved, we derived the new expression
			\tiny
			$p(\vy | \vgamma) = K(n) \left(\frac{n + 1}{1 + p_\vgamma}\right)^{(n-p_\vgamma-1)/2} \frac{[1 + L (1 - R^2_\vgamma)]^{-(n-1)/2}}{p_\vgamma + 1} {}_2 F_1 \left[ \frac{n-1}{2}, 1; \frac{p_\vgamma + 3}{2}; 
			\frac{R^2_\vgamma}{1 + L(1 - R^2_\vgamma)} \right]$ \\
			\small
			where $L = (1 + n)/(1 + p_\vgamma) - 1$.
	\end{itemize}
\end{frame}

\note{Bayarri calculated the marginal likelihood given $\vgamma$ for the Robust Bayarri prior.
			But this expression is not numerically well-behaved.
			We used Euler's transformation and properties of the hypergeometric function to derive a new,
			numerically stable function.}

\end{document}
